Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-02 paper-kelompok/main.tex
grammar
change equation to latex format

    \begin{figure}[htbp]
    \centerline{\includegraphics{fsm.png}}
    \caption{FSM diagram of the portable visible spectrophotometer.}
    \label{fsm}
    \end{figure}

@@

\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Resolution}
Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using the following formula:

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{resolution-eq.png}}
    \label{resolution-eq}
    \end{figure}

>>>>

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.35]{fsm.png}}
    \caption{FSM diagram of the portable visible spectrophotometer.}
    \label{fsm}
    \end{figure}

@@

\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Resolution}
Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using (\ref{resolution}).

\begin{equation}
    resolution=\frac{\lambda_{max} - \lambda_{min}}{n_{pixels}}=\frac{(700 - 400)nm}{393}\approx0.77nm
    \label{resolution}
    \end{equation}
